\documentclass[12pt]{report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage[width=150mm,top=35mm,bottom=25mm,bindingoffset=6mm]{geometry}
\usepackage{amsmath}


\usepackage{fancyhdr}
\pagestyle{fancyplain}% <- use fancyplain instead fancy
\fancyhf{}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{14pt}


\usepackage[style=authoryear,sorting=none]{biblatex}
\addbibresource{references.bib}



\title{On the Volume of the intersection of balls}
\author{Manish Baral}
\date{31 January 2023}
\begin{document}
\pagenumbering{roman} 
\input{titlepage}
\input{abstract}


\tableofcontents

\chapter{Introduction}
\pagenumbering{arabic} 
\input{chapters/Introduction.tex}

\chapter{Literature review and Main results}
\input{chapters/Literature review and Main results.tex}

\chapter{Formula for finding the derivative A}
\input{chapters/Formula for finding the derivative A.tex}


\chapter{Formula for finding the derivative B}
\input{chapters/Formula for finding the derivative B.tex}

\chapter{Voronoi Decomposition}
\input{chapters/Voronoi Decomposition.tex}

\chapter{Formula for Intersection}
\input{chapters/Formula for Intersection.tex}


\chapter{Further discussion}
\input{chapters/Further Discussion.tex}







\chapter*{References}\\
\begin{enumerate}
\item [1] R. Alexander, Lipschitzian mappings and total mean curvature of polyhedral surfaces, no. I, Trans. Amer.Math. Soc. 288 (1985), no. 2, 661–678\\
\item [2] M. Bern, A. Sahai, Pushing disks together—the continuous-motion case, Discr. Comput. Geom. 20 (1998),no. 4, 499–514.\\
\item [3] K. Bezdek and R. Connelly. Pushing disks apart the Kneser-Poulsen conjecture in the plane.
J. Reine Angew. Math., 553:221–236, 2002\\
\item [4] B. Bollobás, Area of the union of disks, Elem. Math. 23 (1968), no. 4, 60–61.\\
\item [5] V. Capoyleas, On the area of the intersection of disks in the plane, Comput. Geom. 6 (1996), no. 6, 393–396.\\
\item [6] V. Capoyleas, J. Pach, On the perimeter of a point set in the plane, Discrete and computational geometry (New Brunswick, NJ), DIMACS Ser. Discr. Math. Theoret. Comput. Sci., Amer. Math. Soc., Providence,RI, 6 (1991), 67–76.\\
\item [7] B. Csikós, On the volume of the union of balls, Discr. Comput. Geom. 20 (1998), no. 4, 449–461\\
\item [8] B. Csikós, On the Hadwiger-Kneser-Poulsen conjecture, Intuitive geometry, Bolyai Soc. Math. Stud. 6, János Bolyai Math. Soc., Budapest (1995), 291–299.\\
\item [9] I.Gorbovickis,"Strict Kneser–Poulsen conjecture for large radii." Geometriae Dedicata 162.1 (2013): 95-107.\\
\item [10] I.Gorbovickis, "The central set and its application to the Kneser–Poulsen conjecture." Discrete & Computational Geometry 59.4 (2018): 784-801.\\
\item [11] I.Gorbovickis, "Kneser-Poulsen conjecture for a small number of intersections." arXiv preprint arXiv:1006.0529 (2010).\\
\item [12] M. Gromov, Monotonicity of the volume of intersections of balls, Geometrical aspects of functional analysis 85–86, Springer, Lect. Notes Math. 1267 (1987), 1–4\\
\item [13] H. Hadwiger, Ungelöste Probleme No. 11, Elem. Math. 11 (1956), 60–61\\
\item [14] V. Klee, V., S. Wagon, Old and new unsolved problems in plane geometry and number theory, 11. Mathematical Association of America, Washington, DC, The Dolciani Mathematical Expositions (1991), 16–20,86–90, 274–278\\
\item [15] M. Kneser, Einige Bemerkungen über das Minkowskische Flächenmass, Arch. Math. 6 (1955), 382–390.
\item [16] E. T. Poulsen, Problem 10, Math. Scand. 2 (1954), 346.\\
\item [17] H. Edelsbrunner, The union of balls and its dual shape, Discr. Comput. Geom. 13 (1995), no. 3–4, 415–440\\
\item [18] R. Seidel, Exact upper bounds for the number of faces in d-dimensional Voronoi diagrams, DIMACS Ser.Discrete Math. Theoret. Comput. Sci., Amer. Math. Soc., Appl. geom. discr. math. 4 (1991), 517–529\\

\end{enumerate}









\end{document}




